Claret: Using Data Types for Highly Concurrent Distributed Transactions

### 2015-03-14 rmd/paper.Rmd
add copyright & conference info, doi

---
title: 'Claret: Using Data Types for Highly Concurrent Distributed Transactions'
preprint: true

@@

conference:
  name: PaPoC 2015
  location: 'April 21, 2015, Bordeaux, France'
  year: 2015

doi: 0

>>>>

---
title: 'Claret: Using Data Types for Highly Concurrent Distributed Transactions'
documentclass:
  name: sigplanconf
  options: 10pt

@@

conference:
  name: PaPoC'15
  location: 'April 21, 2015, Bordeaux, France'
  year: 2015
  copyrightdata: 978-1-4503-3238-5/15/04

exclusivelicense: true
doi: 2745947.2745951
